Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-03-12 SupportingInformation.Rmd
typo fixed

- Given data $(x_i,y_i)$ for $i=1,\ldots,n$ and a 
one-parameter target copula family $\mathcal{B}(\theta)$ (here $\theta$ denotes the parameter), let $\tau$ be the
Kendall correlation of the $x_i$ with the $y_i$ and find the parameter value $\theta_\tau$ for which 
$\mathcal{B}(\theta_\tau)$ has Kendall correlation $\tau$ (this is possible for the one-parameter copula families of this 
study using the `iTau` function of the `VineCopula` package). 
- Generate data $(a_i,b_i)$, $i=1,\ldots,n$ from 
$\mathcal{B}(\theta_\tau)$. 
- Permute the ordered set $(x_1,\ldots,x_n)$ such that the permutation
$(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$ has $\rank(x_{\sigma_x(i)})$ equal to $\rank(a_i)$ for all $i$, where 
$\rank(x_{\sigma_x(i)})$ is the rank of $x_{\sigma_x(i)}$ in the set $(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$, and
$\rank(a_i)$ is the rank of $a_i$ in the set $(a_1,\ldots,a_n)$ (here $\sigma_x$ is a permutation of the 
indices $1,\ldots,n$). 
- Likewise permute $(y_1,\ldots,y_n)$
such that the permutation
$(y_{\sigma_y(1)},\ldots,y_{\sigma_y(n)})$ has $\rank(y_{\sigma_y(i)})$ equal to $\rank(b_i)$ for all $i$ ($\sigma_y$ is 
another permutation of $1,\ldots,n$).
- The surrogate data set is $(x_{\sigma_x(i)},y_{\sigma_y(i)})$ for $i=1,\ldots,n$.

@@

- Given data $x_i(t)$ for $i=1,\ldots,N$ and $t=1,\ldots,T$, let $\tau_{ij}$ be the Spearman (or Kendall) 
correlation of $x_i(t)$ and $x_j(t)$.
- Calculate the covariance matrix of a multivariate normal distribution with standard-normal
marginals and with pairwise Spearman (or Kendall) correlations equal to the $\tau_{ij}$. This is possible.
using the `iRho` function (or the `iTau` function) of the `VineCopula` package
- Generate data $a_i(t)$ for $i=1,\ldots,N$ and $t=1,\ldots,T$ by taking $T$ independent draws
from the multivariate normal distribution of the previous step.
- For any $i,t$ for which the datum $x_i(t)$ was missing, replace $a_i(t)$ by `NA`.
- For each $k$ and $i$ for which $a_i(t)$ is not `NA`, replace the 
$k$th-smallest (non-`NA`) element of the time series 
$a_i(t)$, $t=1,\ldots,T$ by the $k$th smallest (non-`NA`) 
element of $x_i(t)$, $t=1,\ldots,T$.
Call the result $b_i(t)$. This is a surrogate dataset.

>>>>

- Given data $(x_i,y_i)$ for $i=1,\ldots,n$ and a 
one-parameter target copula family $\mathcal{B}(\theta)$ (here $\theta$ denotes the parameter), let $\tau$ be the
Kendall correlation of the $x_i$ with the $y_i$ and find the parameter value $\theta_\tau$ for which 
$\mathcal{B}(\theta_\tau)$ has Kendall correlation $\tau$ (this is possible for the one-parameter copula families of this 
study using the `iTau` function of the `copula` package). 
- Generate data $(a_i,b_i)$, $i=1,\ldots,n$ from 
$\mathcal{B}(\theta_\tau)$. 
- Permute the ordered set $(x_1,\ldots,x_n)$ such that the permutation
$(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$ has $\rank(x_{\sigma_x(i)})$ equal to $\rank(a_i)$ for all $i$, where 
$\rank(x_{\sigma_x(i)})$ is the rank of $x_{\sigma_x(i)}$ in the set $(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$, and
$\rank(a_i)$ is the rank of $a_i$ in the set $(a_1,\ldots,a_n)$ (here $\sigma_x$ is a permutation of the 
indices $1,\ldots,n$). 
- Likewise permute $(y_1,\ldots,y_n)$
such that the permutation
$(y_{\sigma_y(1)},\ldots,y_{\sigma_y(n)})$ has $\rank(y_{\sigma_y(i)})$ equal to $\rank(b_i)$ for all $i$ ($\sigma_y$ is 
another permutation of $1,\ldots,n$).
- The surrogate data set is $(x_{\sigma_x(i)},y_{\sigma_y(i)})$ for $i=1,\ldots,n$.

@@

- Given data $x_i(t)$ for $i=1,\ldots,N$ and $t=1,\ldots,T$, let $\tau_{ij}$ be the Spearman (or Kendall) 
correlation of $x_i(t)$ and $x_j(t)$.
- Calculate the covariance matrix of a multivariate normal distribution with standard-normal
marginals and with pairwise Spearman (or Kendall) correlations equal to the $\tau_{ij}$. This is possible.
using the `iRho` function (or the `iTau` function) of the `copula` package
- Generate data $a_i(t)$ for $i=1,\ldots,N$ and $t=1,\ldots,T$ by taking $T$ independent draws
from the multivariate normal distribution of the previous step.
- For any $i,t$ for which the datum $x_i(t)$ was missing, replace $a_i(t)$ by `NA`.
- For each $k$ and $i$ for which $a_i(t)$ is not `NA`, replace the 
$k$th-smallest (non-`NA`) element of the time series 
$a_i(t)$, $t=1,\ldots,T$ by the $k$th smallest (non-`NA`) 
element of $x_i(t)$, $t=1,\ldots,T$.
Call the result $b_i(t)$. This is a surrogate dataset.
